---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# swfscDAS

<!-- badges: start -->
[![Travis build status](https://travis-ci.com/smwoodman/swfscDAS.svg?branch=master)](https://travis-ci.com/smwoodman/swfscDAS)
[![AppVeyor build status](https://ci.appveyor.com/api/projects/status/github/smwoodman/swfscDAS?branch=master&svg=true)](https://ci.appveyor.com/project/smwoodman/swfscDAS)
<!-- badges: end -->

Warning: `swfscDAS` is still under active development! Please consult with the author (sam.woodman@noaa.gov) before using it.

This package contains functions designed for processing and analyzing DAS data generated using the WinCruz program by the Southwest Fisheries Science Center. Functionality currently includes reading DAS data into a data frame, processing this data (extracting state and condition information for each DAS event), and summarizing sighting and effort information. 

## Installation

You can install `swfscDAS` from [GitHub](https://github.com) with:

``` r
# install.packages("devtools")
devtools::install_github("smwoodman/swfscDAS")
```

## DAS format

You can [download the PDF](https://github.com/smwoodman/swfscDAS/blob/master/inst/DAS_Format.pdf) describing the DAS data format requirements of `swfscDAS`.

## Usage

First, you must read and process the DAS data

```{r example}
library(swfscDAS)
# Get file paths of sample files included in the package
y <- system.file("das_sample.das", package = "swfscDAS")

# Read and process DAS file, i.e. read DAS data into a data frame and add info columns
y.read <- das_read(y)
y.proc <- das_process(y.read)

# Alternatively, the file path can be passed directly to das_process
y.proc <- das_process(y)
```

Note that `das_read` can read multiple files simultaneously

```{r}
y.read.mult <- das_read(c(y, y))
```

Next, you can summarize the processed DAS data

```{r}
# Summarize sighting information
y.sight <- das_sight(y.proc, mixed.multi = TRUE)

# Summarize effort - coming soon..
```

You can also check that your DAS data has accepted formatting and values:

```{r, eval=FALSE}
das_check(y)
```
